---
title: "Topic 7: Word Embeddings"
author: "Clarissa Boyajian"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(here)
library(tidytext)
library(widyr)
library(irlba) #singluar value decomposition
library(broom) # creating search_synonym function
library(textdata)
library(data.table)
library(kableExtra)
```


## Download data

```{r, eval=FALSE}
# run in console
options(timeout = 300)

# read in data (only need to run the lines below once)
download.file('https://nlp.stanford.edu/data/glove.6B.zip', 
              destfile = '../data/glove.6B.zip')
unzip('../data/glove.6B.zip')
```


```{r}
glove_data <- fread(here("data/glove.6B.300d.txt"), 
                    header = FALSE)

glove_data_clean <- glove_data %>%
  column_to_rownames(var = "V1")

# convert df to matrix
glove_matrix <- as.matrix(glove_data_clean)
```


## Question 1
Recreate the analyses in the last three chunks (find-synonyms, plot-synonyms, word-math) with the GloVe embeddings. How are they different from the embeddings created from the climbing accident data? Why do you think they are different?

### Create synonym function

```{r}
# take single word vector and compare to all words in all dimension
# output a similarity score
# similarity score = based on words in the 5 word windows and how they occur together
search_synonyms <- function(word_vectors, selected_vector) {
  
  dat <- word_vectors %*% selected_vector
  
  similarities <- dat %>%
    tibble(token = rownames(dat), similarity = dat[, 1])
  
  similarities %>%
    arrange(-similarity) %>%
    select(c(2, 3))
}
```

### Calculate similary scores for "fall" and "slip"

```{r}
fall <- search_synonyms(glove_matrix, glove_matrix["fall",])

slip <- search_synonyms(glove_matrix, glove_matrix["slip",])
```



### Plot Similarity Score

```{r}
# wrangle data for plotting
plot_data <- slip %>%
  mutate(selected = "slip") %>%
  bind_rows(fall %>%
              mutate(selected = "fall")) %>%
  group_by(selected) %>%
  top_n(15, similarity) %>%
  ungroup %>%
  mutate(token = reorder(token, similarity))
```


```{r, fig.height=3}
# plot 
ggplot(data = plot_data,
       aes(x = token, 
           y = similarity, 
           fill = selected)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~selected, scales = "free") +
  coord_flip() +
  theme(strip.text = element_text(hjust = 0, size = 12)) +
  scale_y_continuous(expand = c(0,0)) +
  labs(x = NULL, 
       y = "Similarity Score",
       title = "What word vectors are most similar to slip or fall?")
```


The synonyms for both "fall" and "slip" are different than those created by the climbing data and have much higher similarity scores. For this data, words with high similarity scores to "fall" seem to be much more general than when we used the climbing data. There are synonyms related to falling down (such as "decline" and "drop"), there are economic terms (such as "prices" and "stocks"), and there is the opposite season ("spring"). Words with high similarity scores to "slip" appear to mostly related to cricked (such as "ball" and "wicket"). It makes sense that the synonyms and similarity scores would be different because we are no longer using climbing specific prose to create our data.


### Word math

```{r}
snow_danger <- glove_matrix["snow",] + glove_matrix["danger",] 

search_synonyms(glove_matrix, snow_danger) %>% 
  head() %>% 
  kbl(caption = "Snow + Danger") %>% 
  kable_styling(latex_options = "HOLD_position")
```

```{r}
no_snow_danger <- glove_matrix["danger",] - glove_matrix["snow",] 

search_synonyms(glove_matrix, no_snow_danger) %>% 
  head() %>% 
  kbl(caption = "Snow - Danger") %>% 
  kable_styling(latex_options = "HOLD_position")
```


## Question 2
Run the classic word math equation, “king” - “man” = ?

```{r}
king_minus_man <- glove_matrix["king",] - glove_matrix["man",] 

search_synonyms(glove_matrix, king_minus_man) %>% 
  head()  %>% 
  kbl(caption = "King - Man") %>% 
  kable_styling(latex_options = "HOLD_position")
```


## Question 3
Think of three new word math equations. They can involve any words you’d like, whatever catches your interest.

```{r}
monster_magic <- glove_matrix["monster",] - glove_matrix["magic",] 

search_synonyms(glove_matrix, monster_magic) %>% 
  head()  %>% 
  kbl(caption = "Monster - Magic") %>% 
  kable_styling(latex_options = "HOLD_position")
```


```{r}
red_anger <- glove_matrix["red",] + glove_matrix["anger",] 

search_synonyms(glove_matrix, red_anger) %>% 
  head()  %>% 
  kbl(caption = "Red + Anger") %>% 
  kable_styling(latex_options = "HOLD_position")
```

```{r}
flower_flour <- glove_matrix["flower",] + glove_matrix["flour",] 

search_synonyms(glove_matrix, flower_flour) %>% 
  head()  %>% 
  kbl(caption = "Flower + Flour") %>% 
  kable_styling(latex_options = "HOLD_position")
```
