---
title: "Topic 6: Topic Analysis"
---

```{r packages}
library(tidyverse)
library(here)
library(pdftools)
library(quanteda)
library(tm)
library(topicmodels)
library(ldatuning)
library(tidytext)
library(reshape2)

```

Load the data

```{r data}
##Topic 6 .Rmd here:https://raw.githubusercontent.com/MaRo406/EDS_231-text-sentiment/main/topic_6.Rmd
#grab data here: 
comments_df<-read_csv(here("data/comments_df.csv"))
```

Now we'll build and clean the corpus

```{r corpus}
epa_corp <- corpus(x = comments_df, text_field = "text")
epa_corp.stats <- summary(epa_corp)
head(epa_corp.stats, n = 25)
tokens <- tokens(epa_corp, remove_punct = TRUE, remove_numbers = TRUE)

# I added some project-specific stop words here
add_stops <- c(stopwords("en"),"environmental", "justice", "ej", "epa", "public", "comment")
tokens_1 <- tokens_select(tokens, pattern = add_stops, selection = "remove")
```

And now convert to a document-feature matrix

```{r dfm}
doc_feature_matric_common <- dfm(tokens_1, tolower = TRUE)
doc_feature_matric <- dfm_wordstem(doc_feature_matric_common)
doc_feature_matric <- dfm_trim(doc_feature_matric, min_docfreq = 2) #remove terms only appearing in one doc (min_termfreq = 10)

print(head(doc_feature_matric))

#remove rows (docs) with all zeros
select_idx <- slam::row_sums(doc_feature_matric) > 0 
doc_feature_matric <- doc_feature_matric[select_idx, ]
#comments_df <- dfm[select_idx, ]
```

We somehow have to come up with a value for k,the number of latent topics present in the data. How do we do this? There are multiple methods. Let's use what we already know about the data to inform a prediction. The EPA has 9 priority areas: Rulemaking, Permitting, Compliance and Enforcement, Science, States and Local Governments, Federal Agencies, Community-based Work, Tribes and Indigenous People, National Measures. Maybe the comments correspond to those areas?

```{r LDA_modeling}
# need to tell model how many topics you think will be in the data
# sort of have to make this up (using 9 becuase EPA has 9 priority areas)
k <- 9 

topicModel_k9 <- LDA(doc_feature_matric, k, 
                     method = "Gibbs", 
                     control = list(iter = 500, verbose = 25))
#nTerms(dfm_comm) 

tmResult <- posterior(topicModel_k9)
attributes(tmResult)
#nTerms(dfm_comm)   
beta <- tmResult$terms   # get beta from results
dim(beta)                # K distributions over nTerms(DTM) terms# lengthOfVocab
terms(topicModel_k9, 10)
```

Some of those topics seem related to the cross-cutting and additional topics identified in the EPA's response to the public comments:

1\. Title VI of the Civil Rights Act of 1964

2.[EJSCREEN](https://www.epa.gov/ejscreen/download-ejscreen-data)

3\. climate change, climate adaptation and promoting greenhouse gas reductions co-benefits

4\. overburdened communities and other stakeholders to meaningfully, effectively, and transparently participate in aspects of EJ 2020, as well as other agency processes

5\. utilize multiple Federal Advisory Committees to better obtain outside environmental justice perspectives

6\. environmental justice and area-specific training to EPA staff

7\. air quality issues in overburdened communities

So we could guess that there might be a 16 topics (9 priority + 7 additional). Or we could calculate some metrics from the data.

```{r LDA_again}
# calculate what initial value of k is most likely
# run series of models (2 topics to 20 topics model)
# apply different metrics and come back with 
result <- FindTopicsNumber(
  doc_feature_matric,
  topics = seq(from = 2, to = 20, by = 1),
  metrics = c("CaoJuan2009",  "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  verbose = TRUE
)

FindTopicsNumber_plot(result)
```


```{r LDA_again}
k <- 7

topicModel_k7 <- LDA(doc_feature_matric, k, method="Gibbs", control=list(iter = 500, verbose = 25))

tmResult <- posterior(topicModel_k7)
terms(topicModel_k7, 10)
theta <- tmResult$topics
beta <- tmResult$terms # probability of each term in each topic
vocab <- (colnames(beta))
```

There are multiple proposed methods for how to measure the best k value. You can [go down the rabbit hole here](#multiple%20proposed%20methods%20for%20measuring%20the%20best%20k%20value.%20You%20can)

```{r top_terms_topic}
comment_topics <- tidy(topicModel_k7, matrix = "beta")

top_terms <- comment_topics %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms
```

```{r plot_top_terms}
top_terms %>%
  mutate(term = reorder(term, beta)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip()
```

Let's assign names to the topics so we know what we are working with. We can name them by their top terms

```{r topic_names}
# name each topic based on 1st 5 terms in topic
top5termsPerTopic <- terms(topicModel_k7, 5)
topicNames <- apply(top5termsPerTopic, 2, paste, collapse = " ")
```

We can explore the theta matrix, which contains the distribution of each topic over each document

```{r topic_dists}
exampleIds <- c(1, 2, 3)
N <- length(exampleIds)

#lapply(epa_corp[exampleIds], as.character) #uncomment to view example text

# get topic proportions from example documents
topicProportionExamples <- theta[exampleIds,]
colnames(topicProportionExamples) <- topicNames
vizDataFrame <- melt(cbind(data.frame(topicProportionExamples), 
                           document = factor(1:N)), 
                     variable.name = "topic", 
                     id.vars = "document")  

ggplot(data = vizDataFrame, 
       aes(x = topic, 
           y = value, 
           fill = document), 
       ylab = "proportion") +
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = N)
```

Here's a neat JSON-based model visualizer

```{r LDAvis}
library(LDAvis)
library("tsne")

svd_tsne <- function(x) tsne(svd(x)$u)

json <- createJSON(
  phi = tmResult$terms, 
  theta = tmResult$topics, 
  doc.length = rowSums(doc_feature_matric), 
  vocab = colnames(doc_feature_matric), 
  term.frequency = colSums(doc_feature_matric),
  mds.method = svd_tsne,
  plot.opts = list(xlab = "", ylab = "")
)

serVis(json)
```

### Assignment:

Either:

A) continue on with the analysis we started:

Run three more models and select the overall best value for k (the number of topics) - include some justification for your selection: theory, FindTopicsNumber() optimization metrics, interpretability, LDAvis

OR

B) use the data you plan to use for your final project:

Prepare the data so that it can be analyzed in the topicmodels package

Run three more models and select the overall best value for k (the number of topics) - include some justification for your selection: theory, FindTopicsNumber() optimization metrics, interpretability, LDAvis